DOM Review Stats and Figures

### 2024-04-17 Analysis/ReviewFigures/ReviewFigures.qmd
Final version for supervisors

  ggplot() +
  geom_sf(aes(fill = Articles), colour = "white", linewidth = 0.01) +
  scale_fill_brewer(palette = "PuBuGn", na.value = "gray40") +
  guides(fill = guide_legend(title = "Number of Articles", nrow = 1)) +
  theme_dark() +
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text = element_blank(), axis.ticks = element_blank())

@@

sampleCoveragePlot <- sampleCoverage |>
  pivot_longer(c(Accept, EstRemaining),
               names_to = "Category", values_to = "Articles") |>
  mutate(Group = case_when(Group == "MacKenzie Cited_2000:2005" ~ "2000-2005",
                           Group == "MacKenzie Cited_2006:2010" ~ "2006-2010",
                           Group == "MacKenzie Cited_2011:2015" ~ "2011-2015",
                           Group == "MacKenzie Cited_2016:2021" ~ "2016-2021",
                           Group == "MacKenzie Cited_2022:2023" ~ "2022-2023")) |>
  mutate(Group = fct(Group, c("2000-2005", 
                              "2006-2010",
                              "2011-2015",
                              "2016-2021",
                              "2022-2023"))) |>

  ggplot() +
  geom_col(aes(x = Group, y = Articles, fill = Category),
           colour = "white", width = 1,
           position = position_stack(reverse = TRUE)) +
  scale_fill_manual(limits = c("Accept", "EstRemaining"),
                    values = c("turquoise4", "gray70"),
                    labels = c("Processed", "Estimated")) +
  scale_y_continuous(limits = c(0, 250), 
                     expand = c(0,0)) +
  labs(title = "Estimated published articles fitting Dynamic Occupancy Models",
       x = "", y = "") +
  theme(legend.position = "top",
        panel.grid = element_blank(),
        title = element_text(size = 14),
        axis.text = element_text(size = 13),
        legend.text = element_text(size = 13))

ggsave("Manuscript/Figures/CoveragePlot.jpeg", sampleCoveragePlot,
       width = 9, height = 4)
```

@@

```{r Focal species bar plot}

@@

speciesPlot <- speciesCounts |>
  ggplot() +
  geom_col(aes(y = Taxa, x = Values, fill = Category)) +
  scale_fill_manual(values = c("darkslategray", "goldenrod", "firebrick4")) +
  labs(x = "", y = "") +
  scale_x_continuous(expand = c(0, 1)) +
  theme(legend.position = "top",
        axis.text.y = element_text(size = 15),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 10), 
        panel.grid = element_blank())

ggsave("Manuscript/Figures/SpeciesPlot.jpeg", speciesPlot, width = 7, height = 5)
```

@@

```{r Study area size}

@@

  studyAreaPlot <- ggplot(studyArea) +
    geom_col(aes(y = StudyArea, x = Articles), fill = "darkslategray") +
    labs(title = "Study Area (square kilometres)", x = "Articles", y = "") +
    scale_x_reverse(expand = c(0,0)) +
    scale_y_discrete(position = "right") +
    theme(panel.grid = element_blank(),
          axis.text = element_text(size = 15), 
          axis.title = element_text(size = 14),
          title = element_text(size = 15), 
          axis.ticks.y = element_blank())

  ggsave("Manuscript/Figures/StudyAreaPlot.jpeg", studyAreaPlot)

@@

```{r Duration fig}

durationPlot <- ggplot(review_Data) +
  geom_histogram(aes(x = Duration), binwidth = 0.2, fill = "turquoise4") +
  geom_vline(aes(xintercept = median(Duration)), 
             colour = "gray30", linetype = 2, linewidth = 3) +
  scale_x_continuous(transform = "log10", 
                     breaks = c(1, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "1 year", "5 years", 
                                "10 years", "20 years", "40 years")) +
  scale_y_continuous(expand = c(0, 0)) + 
  labs(title = "Study duration", x = "", y = "") +
  theme(panel.grid = element_blank(),
        title = element_text(size = 13), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 16, angle = 70, 
                                   hjust = 1, vjust = 1))
ggsave("Manuscript/Figures/Duration.jpeg", durationPlot, 
       height = 4, width = 7)
```

```{r Sites fig}
sitesPlot <- review_Data |>
  mutate(Sites = as.numeric(Sites)) |>

  ggplot() +
  geom_histogram(aes(x = Sites), binwidth = 0.1, fill = "turquoise4") +
  geom_vline(aes(xintercept = median(Sites, na.rm = TRUE)), 
             colour = "gray30", linetype = 2, linewidth = 3) +
  scale_x_continuous(transform = "log10",
                     breaks = c(5, 10, 25, 50, 100, 500, 1000, 10000)) +
  scale_y_continuous(expand = c(0, 0)) + 
  labs(title = "Number of sites", x = "", y = "") +
  theme(panel.grid = element_blank(),
        title = element_text(size = 13), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 16, angle = 70, 
                                   hjust = 1, vjust = 1))
ggsave("Manuscript/Figures/Sites.jpeg", sitesPlot, 
       height = 4, width = 7)
```

@@

@@

covParamPlot <- covariates_clean |>
  mutate(Type = case_when(Type == "E-ANTH" ~ "Anthropogenic",
                          Type == "E-CLIM" ~ "Climate/Weather",
                          Type == "E-DIS" ~ "Disaster/Disturbance",
                          Type == "E-HTAQ" ~ "Habitat (Aquatic)",
                          Type == "E-HTT" ~ "Habitat (Terrestrial)",
                          Type == "E-HYD" ~ "Hydrologic",
                          Type == "E-SEAS" ~ "Phenologic",
                          Type == "E-TOPO" ~ "Topographic",
                          Type == "CONN" ~ "Connectivity",
                          Type == "GEOM" ~ "Site geometry",
                          Type == "INT" ~ "Biotic interaction",
                          Type == "SEAS" ~ "Primary occasion",
                          Type == "SITE" ~ "Site",
                          Type == "SP" ~ "Species",
                          Type == "SURV" ~ "Survey detail",
                          .default = Type)) |>
  mutate(Type_cat = case_when(Type %in% c("Habitat (Terrestrial)",
                                          "Habitat (Aquatic)",
                                          "Hydrologic", 
                                          "Climate/Weather",
                                          "Disaster/Disturbance",
                                          "Topographic",
                                          "Phenologic",
                                          "Anthropogenic",
                                          "Biotic interaction") ~ "Env",
                              .default = "Other")) |>
  summarise(Covariates = case_when("NONE" %in% Type ~ 0,
                                   .default = n()), 
            .by = c(ID, Parameter, Type_cat)) |>
  filter(Parameter != "Occupancy") |>
  complete(nesting(ID, Parameter), 
           Type_cat, fill = list(Covariates = 0)) |>
  mutate(Parameter = fct(Parameter, 
                         levels = c("InitialOccupancy",
                                    "Colonisation", "Extinction",
                                    "Detection"))) |>

  ggplot() +
  geom_boxplot(aes(x = Covariates, y = Type_cat, 
                   colour = Type_cat, fill = Type_cat),
               alpha = 0.5, outliers = FALSE, staplewidth = 0.5) +
  facet_grid(rows = vars(Parameter), switch = "y") +
  scale_colour_manual("Covariate type",
                      values = c("seagreen4", "darkslategray"),
                      labels = c("Environmental", "Other")) +
  scale_fill_manual("Covariate type",
                      values = c("seagreen4", "darkslategray"),
                      labels = c("Environmental", "Other")) +
  labs(title = "Covariate quantity by parameter", 
       x = "Number of covariates considered", y = "") +
  theme(strip.text.y.left = element_text(angle = 0, size = 14, hjust = 1),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        legend.position = "bottom",
        title = element_text(size = 13),
        axis.title.x = element_text(size = 13),
        legend.text = element_text(size = 13))

@@

```{r Covs by objective}

covariates_clean |>
  summarise(Covariates = case_when("NONE" %in% Type ~ 0,
                                   .default = n()), 
            .by = c(ID, Parameter)) |>
  summarise(Covariates = sum(Covariates),
            .by = ID) |>
  left_join(review_Data, by = "ID") |>
  mutate(Predict = if_else(Spatial == "Y" | Future == "Y",
                           "Y", "N")) |>
  pivot_longer(c(Hypothesis, Methods, Parameters, Predict),
               names_to = "Objective", values_to = "ObjIncluded") |>
  filter(ObjIncluded == "Y") |>
  summarise(MedianCovs = median(Covariates), n = n(),
            .by = Objective)

```{r percent polynomial}

covariates_clean |>
  mutate(Polynomial = case_when(Complexity %in% c("Quadratic", "Quadratic + Interaction") ~ 1,
                                .default = 0),
         Interaction = case_when(Complexity %in% c("Interaction", "Quadratic + Interaction") ~ 1,
                                .default = 0)) |>
  summarise(Polynomial = max(Polynomial),
            Interaction = max(Interaction),
            .by = ID) |>
  left_join(review_Data, by = "ID") |>
  mutate(Predict = if_else(Spatial == "Y" | Future == "Y",
                           "Y", "N")) |>
  pivot_longer(c(Hypothesis, Methods, Parameters, Predict),
               names_to = "Objective", values_to = "ObjIncluded") |>
  filter(ObjIncluded == "Y") |>
  summarise(Polynomial = sum(Polynomial)/n(),
            Interaction = sum(Interaction)/n(),
            n = n(),
            .by = Objective)

```{r select}

review_Data |>
  separate_longer_delim(Selection, ", ") |>  
  mutate(Predict = if_else(Spatial == "Y" | Future == "Y",
                           "Y", "N")) |>
  pivot_longer(c(Hypothesis, Methods, Parameters, Predict),
               names_to = "Objective", values_to = "ObjIncluded") |>
  filter(ObjIncluded == "Y") |>
  mutate(total = length(unique(ID)),
         .by = Objective) |>
  summarise(n = n(), total = mean(total),
            .by = c(Objective, Selection)) |>
  mutate(frac = 1-(n/total)) |>
  filter(Selection == "APrioriS")

```{r eval}

review_Data |>
  separate_longer_delim(Evaluation, ", ") |>  
  mutate(Predict = if_else(Spatial == "Y" | Future == "Y",
                           "Y", "N")) |>
  pivot_longer(c(Hypothesis, Methods, Parameters, Predict),
               names_to = "Objective", values_to = "ObjIncluded") |>
  filter(ObjIncluded == "Y") |>
  mutate(total = length(unique(ID)),
         .by = Objective) |>
  summarise(n = n(), total = mean(total),
            .by = c(Objective, Evaluation)) |>
  mutate(frac = n/total) |>
  arrange(Objective)

@@

  ggplot() +
  geom_col(aes(x = Selection, y = fraction, fill = Bayesian)) +
  facet_grid(cols = vars(Bayesian)) + 
  scale_fill_manual(values = c("darkorange3", "turquoise4")) +
  scale_y_continuous(limits = c(0, 0.8), expand = c(0, 0)) +
  scale_x_discrete(labels = c("Single\nmodel",
                              "Candidate\nsuite",
                              "Stepwise\nselection",
                              "Exhaustive\nselection",
                              "Simple", "Other\nmethod")) +
  labs(title = "Model selection methods",
       x = "", y = "Fraction of articles") +
  theme(panel.grid = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15),
        strip.text = element_text(size = 14),
        axis.text.y = element_text(size = 13),
        axis.text.x = element_text(size = 11),
        axis.title.y = element_text(size = 13))

ggsave("Manuscript/Figures/SelectionFigure.jpeg",
       selectFigure, width = 10, height = 4)
```

>>>>

  ggplot() +
  geom_sf(aes(fill = Articles), colour = "white", linewidth = 0.01) +
  scale_fill_brewer(palette = "PuBuGn", na.value = "gray40") +
  guides(fill = guide_legend(title = "Number of Articles", nrow = 1)) +
  theme_dark() +
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text = element_blank(), axis.ticks = element_blank()) 
countries_map

@@

prelimCoverage <- review_Data |>
  filter(Query != "Mackenzie") |>
  summarise(Prelim = n(), .by = Strata)

sampleCoveragePlot <- sampleCoverage |>
  mutate(Group = case_when(Group == "MacKenzie Cited_2000:2005" ~ "2000-2005",
                           Group == "MacKenzie Cited_2006:2010" ~ "2006-2010",
                           Group == "MacKenzie Cited_2011:2015" ~ "2011-2015",
                           Group == "MacKenzie Cited_2016:2021" ~ "2016-2021",
                           Group == "MacKenzie Cited_2022:2023" ~ "2022-2023")) |>
  mutate(Group = fct(Group, c("2000-2005", 
                              "2006-2010",
                              "2011-2015",
                              "2016-2021",
                              "2022-2023"))) |>
  left_join(prelimCoverage, by = join_by("Group" == "Strata")) |>
  pivot_longer(c(Accept, Prelim, EstRemaining),
               names_to = "Category", values_to = "Articles") |>
  mutate(Category = fct(Category,
                        levels = c("Prelim", "Accept", "EstRemaining"))) |>

  ggplot() +
  geom_col(aes(x = Group, y = Articles, fill = Category),
           colour = "white", width = 1,
           position = position_stack(reverse = TRUE)) +
  scale_fill_manual("",
                    limits = c("Prelim", "Accept", "EstRemaining"),
                    values = c("darkslategray", "turquoise4", "gray70"),
                    labels = c("Preliminary", "Secondary", "Estimated articles")) +
  scale_y_continuous(limits = c(0, 300), 
                     expand = c(0,0)) +
  labs(title = "Estimated published articles fitting Dynamic Occupancy Models",
       x = "", y = "") +
  theme(legend.position = "top",
        panel.grid = element_blank(),
        title = element_text(size = 14),
        axis.text = element_text(size = 13),
        legend.text = element_text(size = 13))
sampleCoveragePlot

ggsave("Manuscript/Figures/CoveragePlot.jpeg", sampleCoveragePlot,
       width = 9, height = 4)
sampleCoverage
```

## Authorship

```{r Authorship}

review_Data |>

@@

```{r Focal species bar plot}
#| fig-height: 4
#| fig-width: 8

@@

speciesPlot <- speciesCounts |>
  ggplot() +
  geom_col(aes(y = Taxa, x = Values, fill = Category)) +
  scale_fill_manual(values = c("#2E848E", "gray70", "#896EA3")) +
  labs(x = "", y = "") +
  scale_x_continuous(expand = c(0, 1)) +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 24),
        axis.ticks.y = element_blank(),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
speciesPlot

ggsave("Manuscript/Figures/SpeciesPlot.png", speciesPlot, 
       width = 8, height = 4, bg = "transparent")
```

@@

```{r Study area size}
#| fig-width: 7
#| fig-height: 5

@@

 studyAreaPlot <- ggplot(studyArea) +
    geom_col(aes(x = StudyArea, y = Articles), fill = "#2E848E") +
    labs(title = "", x = "", y = "") +
    scale_y_continuous(expand = c(0,0)) +
    scale_x_discrete(labels = c("0-1", "1-10", "10-100",
                                "100-\n1000", "1000-\n10000",
                                "10000-\n100000", "100000-\n1000000",
                                "1000000+")) +
    theme(panel.grid = element_blank(),
          panel.background = element_rect(fill='transparent', color=NA),
          plot.background = element_rect(fill='transparent', color=NA),
          axis.text.x = element_text(size = 23,
                                     angle = 90,
                                     vjust = 0.5, hjust = 1),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y = element_text(size = 20),
          title = element_text(size = 15),
          axis.ticks.x = element_blank())
  studyAreaPlot

  ggsave("Manuscript/Figures/StudyAreaPlot.png",
         studyAreaPlot,
         width = 7, height = 5,
         bg='transparent')

@@

```{r Duration fig}
#| fig-height: 7
#| fig-width: 4

 durationPlot <- ggplot(review_Data) +
  geom_histogram(aes(y = Duration), binwidth = 0.2, fill = "#2E848E") +
  geom_hline(aes(yintercept = median(Duration)), 
             colour = "gray80", linetype = 2, linewidth = 3) +
  scale_y_continuous(transform = "log10", 
                     breaks = c(1, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "1 year", "5 years", 
                                "10 years", "20 years", "40 years")) +
  scale_x_continuous(expand = c(0, 0)) + 
  labs(title = "", x = "", y = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        title = element_text(size = 13), 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 20))
durationPlot

ggsave("Manuscript/Figures/Duration.jpeg", durationPlot, 
       height = 4, width = 7)
```

```{r Sites fig}
#| fig-width: 7
#| fig-height: 4

sitesPlot <- review_Data |>
  mutate(Sites = as.numeric(Sites)) |>

  ggplot() +
  geom_histogram(aes(x = Sites), binwidth = 0.1, fill = "turquoise4") +
  geom_vline(aes(xintercept = median(Sites, na.rm = TRUE)), 
             colour = "gray30", linetype = 2, linewidth = 3) +
  scale_x_continuous(transform = "log10",
                     breaks = c(5, 10, 25, 50, 100, 500, 1000, 10000)) +
  scale_y_continuous(expand = c(0, 0)) + 
  labs(title = "Number of sites", x = "", y = "") +
  theme(panel.grid = element_blank(),
        title = element_text(size = 13), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 16, angle = 70, 
                                   hjust = 1, vjust = 1))
sitesPlot

ggsave("Manuscript/Figures/Sites.jpeg", sitesPlot, 
       height = 4, width = 7)
```

@@

```{r Covariate type table}
covType_overall <- covariates_clean |>
  select(ID, Type) |>
  mutate(Included = 1, Total = length(unique(ID))) |>
  distinct() |>
  complete(ID, Type, fill = list(Included = 0)) |>
  summarise(Articles = sum(Included),
            Total = max(Total, na.rm = TRUE),
            .by = Type) |>
  mutate(Proportion = round(Articles/Total, 2)) |>
  select(Type, Overall_Proportion = Proportion)

covType_psi <- covariates_clean |>
  filter(Parameter == "InitialOccupancy") |>
  select(ID, Type) |>
  mutate(Included = 1, Total = length(unique(ID))) |>
  distinct() |>
  complete(ID, Type, fill = list(Included = 0)) |>
  summarise(Articles = sum(Included),
            Total = max(Total, na.rm = TRUE),
            .by = Type) |>
  mutate(Proportion = round(Articles/Total, 2)) |>
  select(Type, InitOcc_Proportion = Proportion)

covType_gamma <- covariates_clean |>
  filter(Parameter == "Colonisation") |>
  select(ID, Type) |>
  mutate(Included = 1, Total = length(unique(ID))) |>
  distinct() |>
  complete(ID, Type, fill = list(Included = 0)) |>
  summarise(Articles = sum(Included),
            Total = max(Total, na.rm = TRUE),
            .by = Type) |>
  mutate(Proportion = round(Articles/Total, 2)) |>
  select(Type, Colonisation_Proportion = Proportion)

covType_epsilon <- covariates_clean |>
  filter(Parameter == "Extinction") |>
  select(ID, Type) |>
  mutate(Included = 1, Total = length(unique(ID))) |>
  distinct() |>
  complete(ID, Type, fill = list(Included = 0)) |>
  summarise(Articles = sum(Included),
            Total = max(Total, na.rm = TRUE),
            .by = Type) |>
  mutate(Proportion = round(Articles/Total, 2)) |>
  select(Type, Extinction_Proportion = Proportion)

covType_detection <- covariates_clean |>
  filter(Parameter == "Detection") |>
  select(ID, Type) |>
  mutate(Included = 1, Total = length(unique(ID))) |>
  distinct() |>
  complete(ID, Type, fill = list(Included = 0)) |>
  summarise(Articles = sum(Included),
            Total = max(Total, na.rm = TRUE),
            .by = Type) |>
  mutate(Proportion = round(Articles/Total, 2)) |>
  select(Type, Detection_Proportion = Proportion)

covObserved <- covariates_clean |>
  filter(Type != "NONE") |>
  mutate(Observed = case_when(Measurement == "Observed" ~ 1,
                              .default = 0)) |>
  mutate(Total = n(), .by = Type) |>
  summarise(Observed = sum(Observed),
            .by = c(Type, Total)) |>
  mutate(Proportion_Observed = round(Observed/Total, 2)) |>
  select(Type, Proportion_Observed)

covDynamic <- covariates_clean |>
  filter(Type != "NONE") |>
  filter(Parameter %in% c("Detection", "Colonisation", "Detection")) |>
  mutate(Dynamic = case_when(Variation %in% c("Year",
                                              "Site-Year",
                                              "Site-Year-Survey") ~ 1,
                              .default = 0)) |>
  mutate(Total = n(), .by = Type) |>
  summarise(Dynamic = sum(Dynamic),
            .by = c(Type, Total)) |>
  mutate(Proportion_Dynamic = round(Dynamic/Total, 2)) |>
  select(Type, Proportion_Dynamic)

covPolynomial <- covariates_clean |>
  filter(Type != "NONE") |>
  mutate(Polynomial = case_when(Complexity %in% c("Quadratic",
                                                  "Quadratic + Interaction",
                                                  "Other") ~ 1,
                                .default = 0)) |>
  mutate(Total = n(), .by = Type) |>
  summarise(Polynomial = sum(Polynomial),
            .by = c(Type, Total)) |>
  mutate(Proportion_Polynomial = round(Polynomial/Total, 2)) |>
  select(Type, Proportion_Polynomial)

covInteract <- covariates_clean |>
  filter(Type != "NONE") |>
  mutate(Interact = case_when(Complexity %in% c("Interaction",
                                                  "Quadratic + Interaction") ~ 1,
                                .default = 0)) |>
  mutate(Total = n(), .by = Type) |>
  summarise(Interact = sum(Interact),
            .by = c(Type, Total)) |>
  mutate(Proportion_Interact = round(Interact/Total, 2)) |>
  select(Type, Proportion_Interact)

covType_table <- covType_overall |>
  full_join(covType_psi, by = "Type") |>
  full_join(covType_gamma, by = "Type") |>
  full_join(covType_epsilon, by = "Type") |>
  full_join(covType_detection, by = "Type") |>
  full_join(covDynamic, by = "Type") |>
  full_join(covObserved, by = "Type") |>
  full_join(covPolynomial, by = "Type") |>
  full_join(covInteract, by = "Type") |>

  filter(!Type %in% c("NONE", "OTHER", "SP", "UNSPECIFIED", "SITE")) |>
  mutate(Category = case_when(Type %in% c("E-ANTH", "E-CLIM", "E-DIS",
                                          "E-HTAQ", "E-HTT", "E-HYD",
                                          "E-SEAS", "E-TOPO", "INT") ~ "Environmental",
                              .default = "Other")) |>
  mutate(Type = case_when(Type == "E-ANTH" ~ "Anthropogenic",
                          Type == "E-CLIM" ~ "Climate/Weather",
                          Type == "E-DIS" ~ "Disaster/Disturbance",
                          Type == "E-HTAQ" ~ "Habitat (Aquatic)",
                          Type == "E-HTT" ~ "Habitat (Terrestrial)",
                          Type == "E-HYD" ~ "Hydrologic",
                          Type == "E-SEAS" ~ "Phenology",
                          Type == "E-TOPO" ~ "Topography",
                          Type == "CONN" ~ "Connectivity",
                          Type == "INT" ~ "Biotic Interaction",
                          Type == "GEOM" ~ "Site geometry",
                          Type == "SEAS" ~ "Season",
                          Type == "SURV" ~ "Survey effect"))

kable(covType_table)
write_csv(covType_table, "Manuscript/Figures/CovariateTable.csv")
```

```{r Objectives table}

objs_df <- review_Data |> 
  select(ID, Parameters, Hypothesis, Drivers, Predict, Methods, 
         Selection, Evaluation) |>
  mutate(Any = "Y") |>
  pivot_longer(c(Parameters, Hypothesis, Drivers, Predict, Methods, Any),
               names_to = "Objective", values_to = "Included") |>
  filter(Included == "Y")

covs_summary <- covariates_clean |>
  mutate(Polynomial = case_when(Complexity %in% c("Quadratic",
                                                  "Quadratic + Interaction",
                                                  "Other") ~ 1,
                                .default = 0)) |>
  mutate(Interact = case_when(Complexity %in% c("Interaction",
                                                  "Quadratic + Interaction") ~ 1,
                                .default = 0)) |>
  select(ID, Parameter, Type, Polynomial, Interact) |>
  summarise(Covs = case_when("NONE" %in% Type ~ 0,
                             .default = n()),
            Polynomial = max(Polynomial),
            Interact = max(Interact),
            .by = c(ID, Parameter)) |>
  summarise(Covariates = sum(Covs),
            Polynomial = max(Polynomial),
            Interact = max(Interact),
            .by = ID)

objTable <- objs_df |>
  left_join(covs_summary, by = "ID") |>
  mutate(OverallTotal = length(unique(ID))) |>
  mutate(ObjTotal = length(unique(ID)),
         .by = Objective) |>
  mutate(ObjEval = case_when(str_detect(Evaluation, "GOF") ~ 1,
                             str_detect(Evaluation, "InSampleVal") ~ 1,
                             str_detect(Evaluation, "OutSampleVal") ~ 1,
                             .default = 0)) |>
  mutate(Select = case_when(Selection != "APrioriS" ~ 1,
                            .default = 0)) |>
  summarise(ObjTotal = mean(ObjTotal),
            OverallTotal = mean(OverallTotal),
            MedianCovs = median(Covariates, na.rm = TRUE),
            Poly = sum(Polynomial), Int = sum(Interact), 
            Eval = sum(ObjEval), Select = sum(Select),
            .by = Objective)|>
  mutate(ObjProportion = ObjTotal/OverallTotal,
         ProbPoly = Poly/ObjTotal,
         ProbInt = Int/ObjTotal,
         ProbEval = Eval/ObjTotal,
         ProbSelect = Select/ObjTotal) |>
  select(Objective, Articles = ObjTotal, ArticlesProp = ObjProportion,
         MedianCovs, ProbPoly, ProbInt, ProbEval, ProbSelect) 
kable(objTable)

write_csv(objTable, "Manuscript/Figures/ObjectiveTable.csv")
```

@@

covParamData <- covariates_clean |>
  summarise(Covariates = case_when("NONE" %in% Type ~ 0,
                                   .default = n()), 
            .by = c(ID, Parameter)) |>
  filter(Parameter != "Occupancy") |>
  mutate(Parameter = case_when(Parameter == "InitialOccupancy" ~ "Initial Occupancy",
                               .default = Parameter)) |>
  mutate(Parameter = fct(Parameter, 
                         levels = c("Initial Occupancy",
                                    "Colonisation", "Extinction",
                                    "Detection"))) |>
  mutate(Covariates = case_when(Covariates > 15 ~ 15,
                                .default = Covariates)) |>
  mutate(MedianCovs = mean(Covariates),
         .by = Parameter)

covParamPlot <- covParamData |>
  ggplot() +
  geom_histogram(aes(x = Covariates, fill = Parameter), binwidth = 1) +
  facet_grid(rows = vars(Parameter), switch = "y") +
  labs(title = "Covariate quantity by parameter", 
       x = "Number of covariates considered", y = "") +
  scale_x_continuous(breaks = c(0, 5, 10, 15),
                     labels = c("0", "5", "10", "15+")) +
  scale_y_continuous(position = "right") +
  scale_fill_manual(values = c("turquoise4", "turquoise4", "turquoise4", "orchid4")) +
  theme(strip.text.y.left = element_text(angle = 0, size = 12, hjust = 1),
        panel.grid = element_blank(),
        #axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        legend.position = "none",
        title = element_text(size = 13),
        axis.text = element_text(size = 13),
        axis.title.x = element_text(size = 13),
        legend.text = element_text(size = 13)) 
covParamPlot

@@

@@

  ggplot() +
  geom_col(aes(x = Selection, y = fraction, fill = Bayesian)) +
  facet_grid(cols = vars(Bayesian)) + 
  scale_fill_manual(values = c("darkorange3", "turquoise4")) +
  scale_y_continuous(limits = c(0, 0.8), expand = c(0, 0)) +
  scale_x_discrete(labels = c("Single\nmodel",
                              "Candidate\nsuite",
                              "Procedural\nselection",
                              "Exhaustive\nselection",
                              "Simple\nprecursor", "Other\nmethod")) +
  labs(title = "Model selection methods",
       x = "", y = "Proportion of articles") +
  theme(panel.grid = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15),
        strip.text = element_text(size = 14),
        axis.text.y = element_text(size = 13),
        axis.text.x = element_text(size = 11),
        axis.title.y = element_text(size = 13)) 
selectFigure
ggsave("Manuscript/Figures/SelectionFigure.jpeg",
       selectFigure, width = 10, height = 4)
```
